Future challenges for Research Software Engineering

### 2025-04-17 future_challenges_for_RSEng.tex
fixes

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karlsruhe\cite{Goth2025EndRSEng}.
Therefore it stems from a discussion among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item you like to read,
\item gives you something to think about,
\item motivates you to work on creating this better future.
\end{itemize}
In order to structure the discussion, we decided on a imaginable setting ten years from now. 
In this world we will consider the dimensions of 
\begin{itemize}
\item Evolution of the term RSEs
\item The development of academic institutions
\item How will academic education have transformed by then
\item Ethics and social considerations
\end{itemize}
In each aspect we will quickly summarise on what we want to have achieved by then, and what will be the challenges that arise from that.

\section{The Situation}
In order to give a more explicit setting, imagine a world ten years from now.
Not too much, to be overwhelmingly far in the future, but distant enough for some changes to occur.
Over this timeframe Kim and Kay
were able to ride the waves of their career in Research Software Engineering and are now pondering early retirement on a sunset blessed beach.
But the world has moved on.
When they look back, what will they see as problems which are now solved?
Which tasks are persisting, where they are now happy that a younger generation is now taking up the baton and carries forward their work.
What issues have newly emerged, where they are now just happy to say: “Oh well… My successor takes care of that”.

>>>>

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karlsruhe\cite{Goth2025EndRSEng}.
Therefore it stems from a discussion among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item you like to read,
\item gives you something to think about,
\item motivates you to work on creating this better future.
\end{itemize}
In order to structure the discussion, we decided on a imaginable setting ten years from now. 
In this world we will consider the dimensions of 
\begin{itemize}
\item Evolution of the term RSEs
\item The development of academic institutions
\item What will the impact of AI be to the work of RSEs?
\item How will academic education have transformed by then
\item Ethics and social considerations
\end{itemize}
In each aspect we will quickly summarise on what we want to have achieved by then, and what will be the challenges that arise from that.

\section{The Situation}
In order to give a more explicit setting, imagine a world ten years from now.
Not too much, to be overwhelmingly far in the future, but distant enough for some changes to occur.
Over this timeframe Kim\cite{Anzt2021} and Kay\cite{competencies-F1000}
were able to ride the waves of their career in Research Software Engineering and are now pondering early retirement on a sunset blessed beach.
But the world has moved on.
When they look back, what will they see as problems which are now solved?
Which tasks are persisting, where they are now happy that a younger generation is now taking up the baton and carries forward their work.
What issues have newly emerged, where they are now just happy to say: “Oh well… My successor takes care of that”.
\begin{story}{Introduction}{intro}
In order to bring this future to life these two personas will accompany us and we will shed light on certain aspects
of their future in respective small story boxes.
 \end{story}
